
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 15: Writing a function - Conditional Statement"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment15.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

#### NOTICE: Question 7 and 8 are optional. 

-------

1. Write a function to calculate the age of a person.  Give an example to test your function. 

```{r}
age <- function(x)
{
  r = 2021 - x
  print(paste0('You are ', r, '!'))
}
```

```{r}
age(2000)
```

- Input: a number, x, (year born)

- Output: Print out "You are r age". Where r is the age of the person, i.e. 2020 - x. 

Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions_fa21.html#41)

-------

2. Write the following function. Give an example to test your function. 

- Input: a number

- Output: print out: "You input an even number!" if the number is event, or "You input an odd number!" otherwise. 

Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions_fa21.html#45)

```{r}
odd_even <- function(x)
{
  r = ifelse(x %% 2 == 0, "even", "odd")
  print(paste0('You input an ', r, ' number!'))
}
```

```{r}
odd_even(2000)
```

-------

3. Write the following function.  Give an example to test your function. 

- Input: a numeric vector 

- Output:  

  - if the input vector has missing values: return the input vector with missing values replaced by mean
  
  - if the input vector has no missing value: return the same input vector
  
Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions_fa21.html#49)

```{r}
avg_impute <- function(x)
{
  if(is.numeric(x))
  {
    # Find the mode of x
    avg <- mean(x, na.rm = TRUE)
    library(tidyr)
    x <- replace_na(x, avg) 
  }
return(x)
}
```

```{r}
x = c(1,2,1,NA)
x1 <- avg_impute(x)
x1
```

-------

4. Write the following function.  Give an example to test your function. 

- Input: a vector x 

- Output:  The vector x where the missing values replaced by the mean (if x is numeric) or the mode (if x is non-numeric).  If x does not have missing value, return the same vector x. 
```{r}
mm_impute <- function(x)
{
  if(is.numeric(x))
  {
    # Find the mode of x
    avg <- mean(x, na.rm = TRUE)
    library(tidyr)
    x <- replace_na(x, avg) 
  }
  else {
    mode_of_x <- names(sort(-table(x)))[1]
    # Replace the missing by the mode
    library(tidyr)
    x <- replace_na(x, mode_of_x)
  }
return(x)
}
```

```{r}
x = c(1,2,1,"A", NA)
mm_impute(x)
```

Hint: Use If-statement to combine the function in Question 3 and [this function](https://bryantstats.github.io/math421/gganimate/17_writing_functions_fa21.html#49)

-------

5. Write the following function. Give examples to test your function. 

- Input: A data frame of two variables x and y

- Output: 

  - A boxplot of x by y if x is numeric and y is non-numeric
 
  - A boxplot of y by x if y is numeric and x is non-numeric
 
  - print out 'This function cannot visualize your data' otherwise

Hint: 

- [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions_fa21.html#53)
 
- You can refer to this slide to plot a boxplot: https://bryantstats.github.io/math421/slides/6_viz.html#36

```{r}
viz <- function(d)
{
  if(is.numeric(d[[1]])&!is.numeric(d[[2]]))
  {
    d %>% ggplot(aes(x = d[[1]], y = d[[2]]))+
      geom_boxplot()+
      labs(x = names(d)[1], y = names(d)[2])
  }
  else if (!is.numeric(d[[1]])&is.numeric(d[[2]]))
  {
    d %>% ggplot(aes(x = d[[2]], fill = d[[1]]))+
      geom_boxplot()+
      labs(x = names(d)[2], fill = names(d)[1])
  }
  else 
  {
    print('This function cannot visualize your data.')
  }
}
```

```{r}
library("tidyverse")
df = read_csv("titanic.csv")
df1 = df %>% select("Age", "Sex")
df2 = df %>% select("Sex", "Age")
df3 = df %>% select("Sex", "Name")
df4 = df %>% select("Age", "Fare")
```
```{r}
viz(df4)
```

-------
 
6. Combine the function in Question 5 and the function in this example ([Link](https://bryantstats.github.io/math421/gganimate/17_writing_functions_fa21.html#53)) to have a function that can plot all possible cases (2 categorical, 2 numeric, 1 numeric and 1 categorical). 

```{r}
viz2 <- function(d)
{
  if(is.numeric(d[[1]])&is.numeric(d[[2]]))
  {
    d %>% ggplot(aes(x = d[[1]], y = d[[2]]))+
      geom_point()+
      labs(x = names(d)[1], y = names(d)[2])
  }
  else if(is.numeric(d[[1]])&!is.numeric(d[[2]]))
  {
    d %>% ggplot(aes(x = d[[1]], y = d[[2]]))+
      geom_boxplot()+
      labs(x = names(d)[1], y = names(d)[2])
  }
  else if (!is.numeric(d[[1]])&is.numeric(d[[2]]))
  {
    d %>% ggplot(aes(x = d[[2]], fill = d[[1]]))+
      geom_boxplot()+
      labs(x = names(d)[2], fill = names(d)[1])
  }
  else 
  {
    print('This function cannot visualize your data.')
  }
}
```

```{r}
viz2(df4)
```

-------

#### NOTICE: Question 7 and 8 are optional. 

-------

7. Write the following function. Give examples to test your function. 

- Input: 

  - input_data: a clean data frame with a variable name `target`. The `target` variable is also binary. 
  
  - train_percent: a number presenting a proportion of training data. The default train_percent is .8

- Output: the accuracy of the decision model `rpart` where the training data is train_percent. 

-------

8. Write the following function. Give examples to test your function. 

- Input: 

  - input_data: a clean data frame with a variable name `target`. The `target` variable is also binary. 
  
  - train_percent: a number presenting a proportion of training data. The default train_percent is .8

- Output: the plot of variable important by random forest trained by caret. 


---
9. Write the following function. Give examples to test your function. 

- Input: 

  - a data frame that has a text column 
  
  - the name of the text column in the data

- Output: the word cloud plot of the text column

Sample codes

- [Word Cloud codes](https://bryantstats.github.io/math421/text_mining_sample_codes2.html#2_Word_Cloud)

- [A similar function](https://bryantstats.github.io/math421/gganimate/17_writing_functions_fa21_fa21.html#10)


```{r}
wc <-function(df,col)
{
  library(tidyverse)
  library(tidytext)
  library(knitr)
  library(RColorBrewer)

  pal <- brewer.pal(8,"Dark2")
  library(wordcloud) 

  df %>%
    unnest_tokens(input = col, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))
}
```

```{r}
df_mcu = read_csv("twitter_hawkeye.csv")
wc(df_mcu,"text")
```