
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 10: Predictive Modeling - Part 1"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment10.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install the package `mlbench` and use the follows to import the data

```{r}
library(mlbench)
data(PimaIndiansDiabetes)
df <- PimaIndiansDiabetes
```

- Set seed to be 2020. 
- The target variable is `diabetes`
- Partition the data into 80% training and 20% testing.  

```{r}
library(caret)
set.seed(2020)
splitIndex <- createDataPartition(df$diabetes, p = .80, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
```

-------

2. Practice Decision Tree.  Do the follows:

  - Use `rpart` package, create a decision tree with maximum depth of 3. 
``` {r}
library(rpart) #load the rpart package
# Create a tree
tree_model <- rpart(diabetes ~ ., data = df_train,
                 control = rpart.control(maxdepth = 3))
```

  - Calculate the accuracy of the model on the testing data.
```{r}
#predict on testing data
pred <- predict(tree_model, df_test, type = "class")
#Evaluate the predictions
cm <- confusionMatrix(data = pred, reference = df_test$diabetes, positive = "pos")
cm$overall[1]
```

  - Plot the tree
```{r}
library(rattle)
fancyRpartPlot(tree_model)
```
  
  - Plot the variable importance by the tree
```{r}
barplot(tree_model$variable.importance)
```


-------

3. Practice Random Forest.  Do the follows: 

  - Use `randomForest` package, create a random forest of 1000 trees. 
```{r}
library(randomForest)
```
  
  - Calculate the accuracy of the model on the testing data.
```{r}
rf <- train(diabetes~., data=df_train, 
                method = "rf",
                ntree = 1000) 
pred <- predict(rf, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$diabetes, positive = "pos")
cm$overall[1]
```
  
  - Plot the variable importance by the forest
```{r}
plot(varImp(rf))
```

-------

4. Compare the testing accuracy of a forest of 1000 trees and a forest of 2000 trees. 

```{r}
rf1 <- train(diabetes~., data=df_train, 
                method = "rf",
                ntree = 1000) 
pred1 <- predict(rf1, df_test)
cm1 <- confusionMatrix(data = pred1, reference = df_test$diabetes, positive = "pos")
cm1$overall[1]
```

```{r}
rf2 <- train(diabetes~., data=df_train, 
                method = "rf",
                ntree = 2000) 
pred2 <- predict(rf2, df_test)
cm2 <- confusionMatrix(data = pred2, reference = df_test$diabetes, positive = "pos")
cm2$overall[1]
```

-------

5. Using Caret, create a tree with maximum depth of 3 and forest of 1000 trees. Compare the accuracy of these two models.
```{r}
model1 <- train(diabetes~., data=df_train, 
                method = "rpart2",
                maxdepth=3)
pred_tree <- predict(model1, df_test)
cm_tree <- confusionMatrix(data = pred_tree, reference = df_test$diabetes, positive = "pos")
cm_tree$overall[1]
```
```{r}
model2 <- train(diabetes~., data=df_train, 
                method = "rf",
                ntree = 1000) 
pred_rf <- predict(model2, df_test)
cm_rf <- confusionMatrix(data = pred_rf, reference = df_test$diabetes, positive = "pos")
cm_rf$overall[1]
```

-------

6. Plot variable importance by the two models in 5.
```{r}
plot(varImp(model1))
```

```{r}
plot(varImp(model2))
```

-------

7. (Optional - For extra credits only) Use your own selected data.  Do the follows. 

- Handle missing values if any
``` {r}
library(tidyverse)
nba = read_csv("nba2013.csv")

nba$...1 = NULL
nba$player= NULL
nba$pos= NULL
nba$bref_team_id= NULL
nba$g= NULL
nba$fg= NULL
nba$fga= NULL
nba$x3p= NULL
nba$x3pa= NULL
nba$x2p= NULL
nba$x2pa= NULL
nba$fg.= NULL
nba$x3p.= NULL
nba$x2p.= NULL
nba$efg.= NULL
nba$ft.= NULL
nba$orb= NULL
nba$drb= NULL
nba$ft= NULL
nba$fta= NULL
nba$season= NULL
nba$season_end= NULL
```

- Put the variables in the right format (categorical vs. continuous)

```{r}
nba$Allstar = factor(nba$Allstar)
```

- Select a binary target variable (Use can create a binary target variable from a continuous variable).
```{r}
library(caret)
set.seed(2020)
splitIndex <- createDataPartition(nba$Allstar, p = .70, 
                                  list = FALSE)
df_train <- nba[ splitIndex,]
df_test <- nba[-splitIndex,]
```

- Using caret with method `ranger` to train then test the accuracy of a random forest of 1000 trees.

```{r}
model1 <- train(Allstar~., data=df_train, 
                method = "ranger",
               num.trees = 1000)

pred <- predict(model1, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$Allstar, positive = "1")
cm$overall[1]
```