
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 11: Predictive Modeling - Part 2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment11.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

-------

1. Install the package `mlbench` and use the follows to import the data

```{r}
library(mlbench)
data(PimaIndiansDiabetes)
df <- PimaIndiansDiabetes
```

- Set seed to be 2020. 
- The target variable is `diabetes`
- Partition the data into 80% training and 20% testing.  

```{r}
library(caret)
df$diabetes = factor(df$diabetes)

set.seed(2020)
splitIndex <- createDataPartition(df$diabetes, p = .80, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
```


2. Tuning Decision Tree:  Use cross-validation with 10 k-folds to find the maxdepth with the greatest accuracy. Plot the accuracy associated with different maxdepths against the maxdepths. The range to search for maxdepth is from 1 to 10. 

```{r}
tuneGrid = expand.grid(maxdepth = 1:10)

trControl = trainControl(method = "cv",
                         number = 10)
 
tree_approach2 <- train(diabetes~., data=df_train, 
                                method = "rpart2", 
                                trControl = trControl,
                                tuneGrid = tuneGrid)
plot(tree_approach2)
```


3. Make the final decision to select the maxdepth for your decision tree.  Is your selected maxdepth the same as the maxdepth found in 2? 

I selected the maxdepth of 3. Even thought the graph says the depth of 1 is the most accurate, one depth implies that only one variable is used, which makes the model one-dimensional.



```{r}
library(rpart) #load the rpart package
# Create a tree
tree2 <- rpart(diabetes ~ ., data = df_train,
                 control = rpart.control(maxdepth = 3))
```

4. Calculate the accuracy of your decision tree (the decision tree with your selected maxdepth in 3) on the test data. 

```{r}
library(mlbench)
library(caret)
#predict on testing data
pred <- predict(tree2, df_test, type = "class")
#Evaluate the predictions
cm <- confusionMatrix(data = pred, reference = df_test$diabetes, positive = "pos")
cm$overall[1]
```