
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 13: Text Mining"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment13.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


[Sample Codes](text_mining_sample_codes.html)

-------

### Netflix Data

**1.** Download the `netflix_titles` at this [link](data/netflix_titles.csv).  Create a century variable taking two values:

```{r}
library(tidyverse)
df = read_csv('netflix_titles.csv')
df$century = ifelse(df$release_year >=2000, "21", "20")
```

    - '21' if the released_year is greater or equal to 2000, and
    
    - '20' otherwise. 
    
**2. Word Frequency**    

  a. Convert the description to tokens, remove all the stop words. What are the top 10 frequent words of movies/TV Shows in the 20th century.  Plot the bar chart of the frequency of these words. 
  
```{r}
library(knitr)
library(tidytext)
df %>% 
  unnest_tokens(input = description, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(century, word, sort = TRUE) %>% 
  filter(century == "20") %>% 
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(word, n))) +
  geom_col() +
  labs(y = '', x = 'Frequency')
```

  b. What are the top 10 frequent words of movies/TV Shows in the 21st century. Plot the bar chart of the frequency of these words. Plot a side-by-side bar charts to compare the most frequent words by the two centuries. 
```{r}
df %>% 
  unnest_tokens(input = description, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(century, word, sort = TRUE) %>% 
  filter(century == "20") %>% 
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(word, n))) +
  geom_col() +
  labs(y = '', x = 'Frequency')
```
```{r}
df %>%
  unnest_tokens(input = description, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(century, word, sort = TRUE) %>% 
  group_by(century) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder_within(word, by = n, within = century)) %>%
  ggplot(aes(n, word, fill = century)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~century, scales = "free") +
  labs(x = "Frequency",
       y = NULL)+
  scale_y_reordered() 
```

**3. Word Cloud**

  a. Plot the word cloud of the words in the descriptions in the movies/TV Shows in the 20th century.
  
```{r}
library(wordcloud) 
pal <- brewer.pal(8,"Dark2")

df %>%
  filter(century == "20") %>%
  unnest_tokens(input = description, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(word, sort = TRUE) %>%
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))
```
  
  b. Plot the word cloud of the words in the descriptions in the movies/TV Shows in the 21st century. 
  
```{r}
df %>%
  filter(century == "21") %>%
  unnest_tokens(input = description, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(word, sort = TRUE) %>%
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))
```

**4. Sentiment Analysis**

  a. Is movies/TV Shows in the 21st century tends to be more positive than those in 20th century?  Use the sentiment analysis by `Bing` lexicons to address the question. 
```{r}
library(tidyverse)
library(tidytext)
library(knitr)
df %>%
    unnest_tokens(input = description, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(century, word, sort = TRUE) %>%
    group_by(century) %>% 
    inner_join(get_sentiments("bing")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    group_by(century) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(century, n, fill=sentiment))+geom_col(position = 'fill')+
    labs(y='Relative Frequency', x ='')
```
  
  b. Do sentiment analysis using `nrc` and `afinn` lexicons.  Give your comments on the results.
  
```{r}
df %>%
    unnest_tokens(input = description, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(century, word, sort = TRUE) %>%
    group_by(century) %>% 
    inner_join(get_sentiments("nrc")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    group_by(century) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(sentiment, n, fill=century))+geom_col(position = 'fill')+
    labs(y='Relative Frequency', x ='')
```

```{r}
df %>%
    unnest_tokens(input = description, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(century, word, sort = TRUE) %>%
    group_by(century) %>% 
    inner_join(get_sentiments("afinn")) %>%
    mutate(sentiment = value) %>% 
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    group_by(century) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(century, n, fill=factor(sentiment)))+geom_col(position = 'dodge')+
    labs(y='Relative Frequency', fill = 'Sentiment', x = '')
```
**5. Modeling**

  a. Use the description to predict if a movie/TV show is in 20th or 21st century. Give the accuracy and plot the confusion matrix table.

```{r}
library(caret)
library(themis)
library(textrecipes)

# Select data and set target 
df1 <- df %>% 
  mutate(target = century) %>% 
  select(target, description) 

# Convert text data to numeric variables
a <- recipe(target~description,
       data = df1) %>% 
  step_tokenize(description) %>% 
  step_tokenfilter(description, max_tokens = 10) %>% 
  step_tfidf(description) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_smote(target) %>% 
  prep()
df1 <- juice(a)

# Using Caret for modeling
set.seed(2021)
splitIndex <- createDataPartition(df1$target, p = .2, list = FALSE)
df_train <- df1[ splitIndex,]
df_test <- df1[-splitIndex,]

knn <- train(target~., data=df_train, method = "knn")

pred <- predict(knn, df_test)

cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]
```
```{r}
d = data.frame(pred = pred, obs = df_test$target)
library(yardstick)
d %>% conf_mat(pred, obs) %>% autoplot
```
  
  b. Create variable century2 taking three following values. (Hint: You can use the case_when function to do this)
  
```{r}
df$century2 = ifelse(df$release_year >=2000, "21", ifelse(df$release_year >=1950,"second_half_20", "first_half_20"))
```

    - `21` if released_year is greater or equal to 2000
    
    - `second_half_20`if released_year is greater than or equal to 1950 and less than 2000
    
    - `first_half_20` otherwise
    
  Predict century2 using the descriptions. Give the accuracy and plot the confusion matrix table. (Notice that the codes for 8 should still work for this question)
  
```{r}
library(caret)
library(themis)
library(textrecipes)

df2 <- df %>% 
  mutate(target = century2) %>% 
  select(target, description)

a <- recipe(target~description,
       data = df2) %>% 
  step_tokenize(description) %>% 
  step_tokenfilter(description, max_tokens = 10) %>% 
  step_tfidf(description) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_smote(target) %>% 
  prep()

df2 <- juice(a)

# Using Caret for modeling
set.seed(2021)
splitIndex <- createDataPartition(df2$target, p = .7, 
                                  list = FALSE)
df_train <- df2[ splitIndex,]
df_test <- df2[-splitIndex,]

knn2 <- train(target~., data=df_train, 
                        method = "knn")

pred <- predict(knn2, df_test)

cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]
```
```{r}
d = data.frame(pred = pred, obs = df_test$target)
library(yardstick)
d %>% conf_mat(pred, obs) %>% autoplot
```

**6.** Create another categorical variable from the data and do the following

```{r}
df$mature = ifelse(df$rating %in%c("TV-MA","NR","UR","NC-17","R"), "1", "0")
```

    - Plot side-by-side word frequency by different categories of the newly created variable

```{r}
df %>%
  unnest_tokens(input = description, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(mature, word, sort = TRUE) %>% 
  group_by(mature) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder_within(word, by = n, within = mature)) %>%
  ggplot(aes(n, word, fill = mature)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~mature, scales = "free") +
  labs(x = "Frequency",
       y = NULL)+
  scale_y_reordered() 
```
    
    - Plot word clouds on different categories of the newly created variable
    
```{r}
df %>%
  filter(mature == "1") %>%
  unnest_tokens(input = description, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(word, sort = TRUE) %>%
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))
```
```{r}
df %>%
  filter(mature == "1") %>%
  unnest_tokens(input = description, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(word, sort = TRUE) %>%
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))
```

    - Do sentiment analysis to compare different categories of the newly created variable

```{r}
df %>%
    unnest_tokens(input = description, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(mature, word, sort = TRUE) %>%
    group_by(mature) %>% 
    inner_join(get_sentiments("nrc")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    group_by(mature) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(sentiment, n, fill=mature))+geom_col(position = 'fill')+
    labs(y='Relative Frequency', x ='')
```

```{r}
df %>%
    unnest_tokens(input = description, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(mature, word, sort = TRUE) %>%
    group_by(mature) %>% 
    inner_join(get_sentiments("afinn")) %>%
    mutate(sentiment = value) %>% 
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    group_by(mature) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(mature, n, fill=factor(sentiment)))+geom_col(position = 'dodge')+
    labs(y='Relative Frequency', fill = 'Sentiment', x = '')
```
  
    - Predict the newly created variable using the description. Give the accuracy and plot the confusion matrix table. 

 
```{r}
library(caret)
library(themis)
library(textrecipes)

df3 <- df %>% 
  mutate(target = mature) %>% 
  select(target, description)

a <- recipe(target~description,
       data = df3) %>% 
  step_tokenize(description) %>% 
  step_tokenfilter(description, max_tokens = 10) %>% 
  step_tfidf(description) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_smote(target) %>% 
  prep()

df2 <- juice(a)

# Using Caret for modeling
set.seed(2021)
splitIndex <- createDataPartition(df2$target, p = .7, 
                                  list = FALSE)
df_train <- df2[ splitIndex,]
df_test <- df2[-splitIndex,]

knn <- train(target~., data=df_train, 
                        method = "knn")

pred <- predict(knn, df_test)

cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]
```
```{r}
d = data.frame(pred = pred, obs = df_test$target)
library(yardstick)
d %>% conf_mat(pred, obs) %>% autoplot
```

-------

### Animal Reviews Data

**7.**  Download the animal reviews data at this [link](data/user_reviews.tsv).  Read the data using `read_tsv()` function.
```{r}
df1 = read_tsv("user_reviews.tsv")
```

**8.** Create a `rating` variable taking value `good` if the grade is greater than 7 and `bad` otherwise. 
```{r}
df1$rating = ifelse(df1$grade > 7, "good", "bad")
```

**9.** Do the follows. Notice that the text information is in the `text` variable. 

    - Plot side-by-side word frequency by different categories of the `rating` variable
```{r}
df1 %>%
  unnest_tokens(input = text, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(rating, word, sort = TRUE) %>% 
  group_by(rating) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder_within(word, by = n, within = rating)) %>%
  ggplot(aes(n, word, fill = rating)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~rating, scales = "free") +
  labs(x = "Frequency",
       y = NULL)+
  scale_y_reordered() 
```
    
    - Plot word clouds on different categories of the `rating` variable

```{r}
df1 %>%
  filter(rating == "good") %>%
  unnest_tokens(input = text, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(word, sort = TRUE) %>%
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))
```
```{r}
df1 %>%
  filter(rating == "bad") %>%
  unnest_tokens(input = text, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  count(word, sort = TRUE) %>%
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))
```
    
    - Do sentiment analysis to compare different categories of the `rating` variable

```{r}
df1 %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(rating, word, sort = TRUE) %>%
    group_by(rating) %>% 
    inner_join(get_sentiments("nrc")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    group_by(rating) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(sentiment, n, fill=rating))+geom_col(position = 'fill')+
    labs(y='Relative Frequency', x ='')
```
```{r}
df1 %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(rating, word, sort = TRUE) %>%
    group_by(rating) %>% 
    inner_join(get_sentiments("afinn")) %>%
    mutate(sentiment = value) %>% 
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    group_by(rating) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(rating, n, fill=factor(sentiment)))+geom_col(position = 'dodge')+
    labs(y='Relative Frequency', fill = 'Sentiment', x = '')
```
    - Predict the rating using the reviews (`text` variable). Give the accuracy and plot the confusion matrix table.

```{r}
df3 <- df1 %>% 
  mutate(target = rating) %>% 
  select(target, text)

a <- recipe(target~text,
       data = df3) %>% 
  step_tokenize(text) %>% 
  step_tokenfilter(text, max_tokens = 10) %>% 
  step_tfidf(text) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_smote(target) %>% 
  prep()

df2 <- juice(a)

# Using Caret for modeling
set.seed(2021)
splitIndex <- createDataPartition(df2$target, p = .7, 
                                  list = FALSE)
df_train <- df2[ splitIndex,]
df_test <- df2[-splitIndex,]

knn <- train(target~., data=df_train, 
                        method = "knn")

pred <- predict(knn, df_test)

cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]
```

```{r}
d = data.frame(pred = pred, obs = df_test$target)
library(yardstick)
d %>% conf_mat(pred, obs) %>% autoplot
```